Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of mixed binary observations

### 2016-07-11 Paper/paper.tex
update fig captions

{\it Left:} This figure shows the median value of the recovered

@@

in the population $N$. There are four family of curves, one corresponding each
to $\lambdans=\{500,1000,1500,2000\}$, with $100$ independent populations
within each family. One curve in each family is highlighted in color, 
representing that it is the same population as was illustrated in

@@

horizontal dash-dotted lines. We observe that within $10-25$ observations, 
the median of the measured cumulative probability distribution for $\lambdans$
will lie within $10\%$ of the true value.
{\it Right:} This figure is identical to the left panel, with the only
difference that the BH masses in each population are restricted to lie
{\it outside} the astrophysical mass-gap (i.e. paradigm B). The difference that

@@

\includegraphics[width=\columnwidth]{plots/LambdaCIWidths90pc_vs_N_AllPopulation.pdf}
\includegraphics[width=\columnwidth]{plots/LambdaCIWidths90pc_vs_N_AstroPopulation.pdf}

@@

These figures show the width of the $90\%$ confidence interval for $\lambdans$
(normalized by its true value), as a function of the number of observed events
$N$. The left column panels show populations sampled under paradigm A, which
allows BH masses to fall within the astrophysical mass-gap, while those on the
right show populations drawn under paradigm B which respects the mass-gap.

@@

decreasing from $2000\rightarrow 500$ as we go from top to bottom. In each panel,
$100$ curves are shown, each corresponding to an independent population draw. The
one colored curve in each panel highlights the population used in
The insets in each panel show the same information, with the ordinate {\it not}
normalized by the true value of $\lambdans$.

@@

of design aLIGO operation~\cite{Abadie:2010cfa}. Further tightening of the
confidence intervals will require $40+$ events.

@@

this figure as a function of the number of observed events $N$.

@@

Finally, we quantitatively explore the dependence of our statistical

>>>>

{\it Top left}: This figure shows the median value of the recovered

@@

in the population $N$. There are four ensembles of curves,
corresponding to $\lambdans=\{500,1000,1500,2000\}$, with a hundred
independent population draws within each ensemble. One curve in each ensemble
is highlighted in color, representing only that it is the same population as 
was discussed in

@@

horizontal dash-dotted lines.
{\it Bottom left}: Here we show the interval of $\lambdans$ values within
which the median measured $\lambdans$ lies for $90\%$ of the populations in
each ensemble shown in the top left panel.
We observe that within $10-25$ observations, the median of the measured 
cumulative probability distribution for $\lambdans$ converges to within $10\%$
of its true value.
{\it Right:} These panels are identical to their counterparts on the left,
with the only difference that the BH masses in each population are restricted
to lie {\it outside} the astrophysical mass-gap (i.e. paradigm B). The
difference that

@@

\includegraphics[width=\columnwidth]{plots/LambdaCIWidths90pc_vs_N_AllPopulation}
\includegraphics[width=\columnwidth]{plots/LambdaCIWidths90pc_vs_N_AstroPopulation}

@@

{\it Left}: This panel shows the width of $\lambdans$ interval within
which the $90\%$ confidence intervals for $\lambdans$ lie, for $90\%$ of 
the populations in each ensemble, as a function of the number of observed events
$N$. Details of how this is calculated are given in the text.
The populations are sampled under paradigm A, which allows BH masses to
fall within the astrophysical mass-gap.

@@

decreasing from $2000\rightarrow 500$ as we go from top to bottom.
{\it Right}: This panel shows populations drawn under paradigm B, which
respects the mass-gap.

@@

of design aLIGO operation~\cite{Abadie:2010cfa}. Further tightening of 
$\lambdans$ confidence intervals will require $40+$ events.

@@

this figure as a function of the number of observed events $N$. The thicker
curve corresponds to the populations discussed in
Fig.~\ref{fig:TT_Lambda_vs_N_CI90_0}.

@@

Here, we quantitatively explore the dependence of our statistical
